Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-11-03 Methods-and-Results.Rmd
AOT-M Methods first draft

The aim of our study is similar to to that of the first study, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts. However, in this second study we collected a substantially larger intensive longitudinal survey study with recently arrived international students in the Netherlands. The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis. Data was collected from November 19th, 2018 through January 6th, 2019.

@@

@@

```{r medicalSampleInfo, include=FALSE}

medicalDemographicSupp <- 
  dtMedical$raw.eligibility %>%
  filter(session %in% dtMedical$full$session) %>%
  select(session, nationality, studentBachMa)
# summarize participant characteristics

@@

```{r studentVarDescr, include=FALSE}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

@@

```{r studentOutVarDescr, include=FALSE}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

@@

\paragraph{Intergroup Contact}

\paragraph{Psychological Needs}

\paragraph{Allport's Conditions}

\paragraph{Perceived Interaction Quality}

\paragraph{Outgroup Attitudes}

>>>>

The aim of our study is similar to that of the first study, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts. However, in this second study we collected a substantially larger intensive longitudinal survey study with recently arrived international students in the Netherlands. The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis. Data was collected from November 19th, 2018 through January 6th, 2019.

@@

The aim of this final study is to extend the previous studies by additionally testing Allport's conditions in an extensive longitudinal design and to compare the predictive powers of Allport's conditions and the core situational need fulfillment. We will, thus, again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts. However, we additionally have the opportunity to also assess the role of Allport's conditions in this and to compare the two approaches (Allport's conditions and core need fulfillment) directly.

For this study we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis. As part of their educational program, the migrants are required to take language courses and interact with patients as part of their medical internships and medical residency. The extensive longitudinal survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations. Data were collected from November 8th, 2019 to January 10th, 2020.

The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B. Correlations and descriptive statistics of the included variables are available in Table \ref{tab:medicalVarDescr} and Table \ref{tab:medicalOutVarDescr}.

@@

```{r medicalSampleInfo, include=FALSE}
# extract demographic information from eligibility questionnaire
medicalDemographicSupp <- 
  dtMedical$raw.eligibility %>%
  filter(session %in% dtMedical$full$session) %>%
  select(session, nationality, studentBachMa)
# summarize participant characteristics

@@

```{r medicalVarDescr, include=FALSE}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

@@

```{r medicalOutVarDescr, include=FALSE}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

@@

\paragraph{Intergroup Contact}The measurement of intergroup contacts was identical to study two. The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max`
(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtMedical$full)` daily diary responses).

\paragraph{Psychological Needs}The measurement of the core situational need and its fulfillment was identical to study two. Similarly, the measurement of the self determination needs was identical to studies one and two.

\paragraph{Allport's Conditions}To measure how much each of the interactions fulfilled Allport's conditions of optimal contact we asked participants to rate how much the interaction had equal status ("\textit{The interaction with [name interaction partner] was on equal footing (same status)}"), a common goal ("\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}"), support of authorities ("\textit{The interaction with [name interaction partner] was voluntary}"), and intergroup cooperation ("\textit{The interaction with [name interaction partner] was cooperative}").

\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to study one.

\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in studies one and two. All survey details are also available in Online Supplemental Materials A and B.

\input{Tables/medicalVarDescr}
\input{Tables/medicalOutVarDescr}

### 2021-11-03 Methods-and-Results.tex
methods and results re-run
AOT-M Methods first draft

>>>>

After receiving ethical approval from the University of Groningen, we
recruited 71 international medical students using a contacts within the
University Medical Department and specifically targeted non-Dutch
students, who had recently arrived in the Netherlands. Participants
reported on their interactions for at least 30 days with two daily
measures (capturing the morning and afternoon). With this design, we
aimed at getting 50-60 measurements per participant (\textit{M} = 57.85,
\textit{SD} = 20.68, \textit{total N} = 4107). As with the previous
study this should offer sufficient power to model processes within
participants and will lend stronger weight to between-participant
results. Participants were compensated for their participation with
partial course credits --- depending on their participation. The sample
consisted of relatively young migrants, who were mostly from the global
north (\(M_{age}\) = 22.68, \(SD_{age}\) = 3.10, 59 women). The sample
fairly accurately describes the local population of international
students.

The study procedure mirrored the setup of studies one and two, in that
it consisted of pre-, daily diary-, and post-measurement. The
participants were invited for daily diary measurements twice a day (at
12 pm and 7pm) for 30 days (\textit{median duration} = 13,
\textit{MAD duration} = 6). General compliance was high (93.30\% filled
daily diary surveys for 31 days or more NEED TO RE-CHECK THIS). The
response rates were approximately equal during mornings (\textit{n} =
2092) and afternoons (\textit{n} = 2015). All key variables in for this
study were part of the short daily diary surveys.

The measurement of intergroup contacts was identical to study two. The
participants recorded between 1--71 (2.13--87.18\% of individual daily
diary measurements; 41.44\% of all 4107 daily diary responses).

The measurement of the core situational need and its fulfillment was
identical to study two. Similarly, the measurement of the self
determination needs was identical to studies one and two.

\paragraph{Allport's Conditions}

To measure how much each of the interactions fulfilled Allport's
conditions of optimal contact we asked participants to rate how much the
interaction had equal status
(``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
a common goal
(``\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}''),
support of authorities
(``\textit{The interaction with [name interaction partner] was voluntary}''),
and intergroup cooperation
(``\textit{The interaction with [name interaction partner] was cooperative}'').

The ratings of the perceived interaction quality was identical to study
one.

Attitudes towards the Dutch majority outgroup was again measured using
the feeling thermometer, as in studies one and two. All survey details
are also available in Online Supplemental Materials A and B.

\input{Tables/medicalVarDescr}
\input{Tables/medicalOutVarDescr}
